\documentclass[10pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{left=0.5in, top=0.4in, right=0.5in, bottom=0.4in}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}

% Custom colors
\definecolor{primary}{RGB}{0, 0, 0}
\definecolor{secondary}{RGB}{80, 80, 80}
\definecolor{links}{HTML}{0056b3}

\hypersetup{
    colorlinks=true,
    linkcolor=links,
    urlcolor=links
}

% Section formatting
\titleformat{\section}
  {\bfseries\large\uppercase}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{10pt}{5pt}

% Style configurations
\pagestyle{empty}
\setlist[itemize]{leftmargin=0.15in, nosep, after=\vspace{4pt}}

\begin{document}

% Header
\begin{center}
    {\Huge \bfseries Mohit Negi} \\ \vspace{4pt}
    \small
    +91-8923645746 \ | \ Kotdwar, Uttarakhand \ | \ \href{mailto:cse24135@iiitkalyani.ac.in}{cse24135@iiitkalyani.ac.in} \\ \vspace{2pt}
    \href{https://linkedin.com}{LinkedIn} \ | \ \href{https://github.com}{GitHub} \ | \ \href{https://codeforces.com}{Codeforces} \ | \ \href{https://kaggle.com}{Kaggle}
\end{center}

\vspace{-10pt}

% Summary
\section{Summary}
Data Science, AI/ML, and Full-Stack Web Development enthusiast with strong skills in Python, SQL, React.js, Node.js, and Machine Learning. Experienced in building end-to-end data-driven applications, recommendation engines, RAG pipelines, and full-stack platforms.

% Education
\section{Education}
\noindent \textbf{Indian Institute of Information Technology, Kalyani} \hfill 2024 -- Present \\
B.Tech in Computer Science and Engineering \hfill CGPA: 9.03 / 10.0

% Technical Skills
\section{Technical Skills}
\begin{description}[leftmargin=0pt, labelwidth=1.3in, align=left, itemsep=2pt, parseitemsep=0pt]
    \item[\textbf{Languages:}] Python, C, C++, Java, JavaScript, SQL
    \item[\textbf{Web Development:}] React.js, Node.js, Express.js, MongoDB, REST APIs, HTML5, CSS3, Bootstrap
    \item[\textbf{Data Analysis \& AI:}] Pandas, NumPy, Scikit-learn, FAISS, NLP, Deep Learning, Exploratory Data Analysis (EDA)
    \item[\textbf{LLM \& RAG Tools:}] LangChain, LangGraph, Vector Databases
    \item[\textbf{Visualization \& Tools:}] Streamlit, Matplotlib, Seaborn, Git, GitHub
    \item[\textbf{Core CS Concepts:}] Data Structures \& Algorithms (DSA), Object-Oriented Programming (OOP)
\end{description}

% Projects
\section{Projects}

\noindent \textbf{Zomato Delivery App (Full-Stack)} \hfill \href{https://tomato-delivery-frontend-16al.onrender.com}{[Live Link]} \\
\textit{React, Node.js, Express, MongoDB, Render}
\begin{itemize}
    \item Designed and developed a fully responsive food delivery platform featuring a client-facing web application, backend API, and a dedicated admin management portal.
    \item Implemented robust CRUD operations for real-time menu management, dynamic shopping cart updates, and secure user data storage.
    \item Deployed the client, admin panel, and backend services separately on Render, utilizing environment variables for secure database connection.
\end{itemize}

\noindent \textbf{LangGraph AI Chatbot} \hfill \href{https://chatbot-cqhq4vpuraen6vxo4g4nt4.streamlit.app/}{[Live Link]} \\
\textit{LangGraph, LangChain, Python, SQLite}
\begin{itemize}
    \item Developed a stateful, agentic conversational chatbot powered by LangGraph to handle multi-turn dialogs and cyclical flow logic.
    \item Integrated session persistence and state management using an SQLite-backed memory saver to maintain conversation history across reloads.
    \item Structured clean branching logic using state variables, enabling dynamic tool invocation based on user query context.
\end{itemize}

\noindent \textbf{Enterprise Knowledge Copilot (RAG)} \hfill \href{https://chatbot-cqhq4vpuraen6vxo4g4nt4.streamlit.app/}{[Live Link]} \\
\textit{RAG, LangChain, FAISS, Streamlit}
\begin{itemize}
    \item Developed a Retrieval-Augmented Generation (RAG) assistant allowing users to upload documents and query knowledge bases.
    \item Utilized text chunking and semantic search with FAISS vector database to retrieve context-aware answers efficiently.
    \item Deployed the user interface on Streamlit, optimizing performance to return answers with references in under 2 seconds.
\end{itemize}

\noindent \textbf{Book Recommendation System} \hfill \href{https://book-recommender-system-5olv.onrender.com/}{[Live Link]} \\
\textit{Machine Learning, Pandas, Cosine Similarity, Flask}
\begin{itemize}
    \item Built an end-to-end recommendation engine utilizing TF-IDF Vectorization and Cosine Similarity to recommend matches out of a database of 10K+ books.
    \item Designed a lightweight Flask backend and a responsive user interface to handle real-time prediction requests.
\end{itemize}

\noindent \textbf{WhatsApp Chat Analyzer} \hfill \href{https://whatsappanalyser-7mxtgbpbvxsytrdynkujd5.streamlit.app/}{[Live Link]} \\
\textit{Python, Regular Expressions, NLP, Streamlit}
\begin{itemize}
    \item Parsed and structured raw text data of 50K+ messages using regular expressions to extract timestamps, authors, and text.
    \item Performed EDA and NLP analysis (Sentiment analysis, Word Cloud, activity heatmap) to visualize messaging trends.
\end{itemize}

% Leadership Experience
\section{Leadership Experience}
\noindent \textbf{AI/ML Lead} \ | \ GDG On Campus, IIIT Kalyani \hfill 2025 -- Present
\begin{itemize}
    \item Conducted hands-on technical workshops on Machine Learning, Deep Learning, and EDA for 100+ students.
    \item Mentored university teams on AI research and Natural Language Processing projects.
\end{itemize}

\noindent \textbf{General Secretary (Technical Affairs)} \ | \ Gymkhana, IIIT Kalyani \hfill 2025 -- Present
\begin{itemize}
    \item Organized college coding hackathons, technical workshops, and coding challenges for over 200 participants.
\end{itemize}

% Achievements & Certifications
\section{Achievements \& Certifications}
\begin{itemize}
    \item \textbf{2nd Runner-Up}, InnovateX Hackathon (GDG IIIT Kalyani) \hfill 2025
    \item \textbf{Winner}, Botball Robotics Competition \& \textbf{2nd Runner-Up}, Maze Solver Robotics \hfill 2025
    \item \textbf{Data Structure \& Algorithms}: Solved 200+ algorithmic challenges across Codeforces & LeetCode.
    \item \textbf{Certification}: Data Analysis with Python -- freeCodeCamp.
\end{itemize}

\end{document}
